{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-31 brains-protocol.tex
Update fig.4 caption for heatmap with numbers of words

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/feature_susceptibilities.png}
    \caption{\textbf{Substitution susceptibility:} average susceptibility to substitution vs. average feature value of a candidate word for substitution, with 95\% asymptotic confidence intervals.
    \TB{Apart from Word frequency (where low-frequency words are more susceptible than high-frequency words), results do not let us conclude either to an effect or to no effect of the features on susceptibility.
    The heatmap on the lower-right, detailing the interaction of Age of acquisition and Number of phonemes on susceptibility, also shows no significant effect once outlier values are discarded.}}
    \label{fig:feature-susceptibilities}
\end{figure*}

>>>>

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/feature_susceptibilities.png}
    \caption{\textbf{Substitution susceptibility:} average susceptibility to substitution vs. average feature value of a candidate word for substitution, with 95\% asymptotic confidence intervals.
    \TB{Apart from Word frequency (where low-frequency words are more susceptible than high-frequency words), results do not let us conclude either to an effect or to no effect of the features on susceptibility.
    The heatmap on the lower-right details the interaction of Age of acquisition and Number of phonemes on susceptibility; susceptibility values are indicated in the cells, and the number of words per cell is indicated in parentheses.
    Once outlier values with only 11 words are discarded, the heatmap shows no significant interaction effect.}}
    \label{fig:feature-susceptibilities}
\end{figure*}
